
\documentclass[a4paper,10pt]{article}
\input{glyphtounicode}
\pdfgentounicode=1
\usepackage{url}
\usepackage{parskip}
\RequirePackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\newcolumntype{C}{>{\centering\arraybackslash}X} 
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.2\textwidth}
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{4pt}{4pt}
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.7}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\usepackage{fontawesome5}


\begin{document}


\pagestyle{empty}
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}



%----------Header--------------


  \begin{tabularx}{\linewidth}{@{} C @{}}

    \Huge{Rahul Kumar} \\[7.5pt]

    \href{https://github.com/rahulkrchaudhary}{\raisebox{-0.05\height}\faGithub\ GitHub} \ $|$ \ 
    \href{https://linkedin.com/in/rahulkrchaudhary}{\raisebox{-0.05\height}\faLinkedin\ Linkedin} \ $|$ \  \ 
    \href{mailto:rahulkrchaudhary12@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ rahulkrchaudhary12@gmail.com} \ $|$ \ 
    \href{tel:+919262685956}{\raisebox{-0.05\height}\faMobile \ +91 9262685956}
    \\
  \end{tabularx}


%----------Education-----------


  \section{Education}
    \resumeSubHeadingListStart
      \resumeSubheading
        {Dayananda Sagar College Of Engineering}{SGPA: 9.65}%
        {B.E in Computer Science (VTU)}{2022 -- 2026}
        \hspace{4pt}
    \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
      \resumeSubheading
        {Sitamarhi Central School, Bihar}{89.\%}
        {CBSE --- Secondary School}{2020 -- 2022} \\
    \resumeSubHeadingListEnd
  \vspace{-10pt}


%----------Skills--------------

\vspace{6pt}
  \section{Skills}
  \begin{tabularx}{\linewidth}{@{}l X@{}}
    \textbf{Languages:} &  \normalsize{Java, MySQL, C/C++ } \\
    \textbf{Frameworks/Technologies:}  &  \normalsize{Andriod Studio, Git, GitHub, VS Code}\\
  \end{tabularx}
  \vspace{-5pt}


%----------Projects------------


  \section{Projects}
    
    \vspace{7pt}
    
  \begin{tabularx}{\linewidth}{ @{}l r@{} }
\vspace{-5pt}
    \textbf{Cab Booking Management System} | \textit{Java, Swing, MySQL} & \hfill \href{https://github.com/rahulkrchaudhary/Cab-Rental-Management}{GitHub} \\
      \multicolumn{1}{@{}X@{}}{
       \begin{itemize}
    \item Developed a Cab Rental Management System in Java using Swing for graphical interface.
    \item Implemented features such as booking cabs, viewing available cabs, and viewing booking history.
    \item Utilized Object-Oriented Programming principles for efficient code organization and maintenance.
    \item Integrated MySQL database for storing and managing cab-related information.
    \item Contributed to enhancing user experience and convenience in accessing transportation services through efficient code design and database management.
\end{itemize}

            }  \\

 \end{tabularx}


%----------Achievements---------


  \section{Achievements and Certifications}


    \begin{tabularx}{\linewidth}{ @{}l r@{} }
      \textbf{Google Cybersecurity} & \hfill \href{https://www.coursera.org/account/accomplishments/professional-cert/GZJ7LQGCFFZF}{Coursera (Mar 2024)}
      \\[3.75pt]
      \multicolumn{2}{@{}X@{}}{An eight course professional certificate program in cybersecurity. Equipped with skills in threat detection, incident response, network security, python automation, SQL etc. }
    \end{tabularx}

    \begin{tabularx}{\linewidth}{ @{}l r@{} }
      \textbf{AI Security Fundamentals} & \hfill \href{https://security.certificates.lakera.ai/credentials/c46521d6-5748-4834-8bac-ecf7913c3ccc}{LakeraAI (Mar 2024)}
      \\[3.75pt]
      \multicolumn{2}{@{}X@{}}{AI Security Course, covering topics such as GenAI threats, cybersecurity frameworks, AI application security, LLM red teaming, and AI governance. }
    \end{tabularx}

    \begin{tabularx}{\linewidth}{ @{}l r@{} }
      \textbf{HackMan v6} & \hfill May 2023 \\[3.75pt]
      \multicolumn{2}{@{}X@{}}{Secured position in top 10 among 50 other teams. Hackman is a Inter-College hackathon conducted by ISE Depart of DSCE College }
    \end{tabularx}


%----------Extracurricular-----


  \section{Extracurricular}

    \begin{tabularx}{\linewidth}{ @{}l r@{} }
      \textbf{PointBlank --- Member} & \hfill Dec 2022 - Present \\[3.75pt]
      \multicolumn{2}{@{}X@{}}{PointBlank is a group of over 80 programmers who work to promote coding culture in colleges by participating in more than 10 contests and organising technical seminars}
    \end{tabularx}
    
    \begin{tabularx}{\linewidth}{ @{}l r@{} }
      \textbf{Arcis --- Member} & \hfill Dec 2022 - Feb 2023 \\[3.75pt]
      \multicolumn{2}{@{}X@{}}{Team Arcis is the Official Aero Design of Dayananda Sagar College of Engineering. They participate in the SAE Aero Design Challenge and AIAA DBF, two of the biggest student design competitions, held annually in USA.}
    \end{tabularx}



    \end{document}
